Proposed Solution

### 2016-11-12 Ennan-Proposal/solutions.tex
stuff

\section{Learner}
\label{sec-learn}

@@

\subsection{Derivation of ConfigC Rules}
\label{subsec-rules}

@@

We chose to employ this approach in our earlier work~\cite{santolucitoCAV} because any rule produced is guaranteed to be a correct rule.
As opposed to a traditional machine learning approach, we have here a formal guarantee of rule coverage.
Furthermore, by design this approach gives a justification (error location) for the classification of a user file as correct or misconfiguration.
This approach is most closely related to version space learning~\cite{mitchell77}, which we discuss further in Sec.~\ref{sec:travis}.

\subsection{Derivation of ConfigV Rules}
In \app's learner module, we release the assumption in the above
solution, which means the rule learning mechanism is tolerant 
enough to accept a dataset of possibly incorrect configuration files.
Rather than manually correcting each file, 
we extend the previous formalism to run probabilistic learning
on our intermediate representations (generated by the translator).
Our probabilistic approaches for learning missing entry, 
ordering, and fine-grained value correlation rules stem 
from existing work with building 
non-probabilistic versions of these rule-learning algorithms. 
For each of these rules, 
we consider all possible permutations of keys that appear in every 
file which are appropriately typed, and for our learning process, calculate the likelihood that each of 
these permutations constitute a rule. 
Rule patterns in the example set that appear frequently are accepted,
so they can be used to evaluate new files.

\begin{figure}[!h]
\begin{small}
\belowdisplayskip=-15pt
\abovedisplayskip=-2pt
\begin{align*}
U ::&\ \text{Unlabeled Learning Set}\\
U =&\ \text{\{Configuration Files in Intermediate Representation\}}\\
LP ::&\ \text{Learned Probabilistic Rules :: \{P\_Rule\}}\\
LP =&\ \{ r\ \mid \Pi file \in C,\ holds(r,file)\ \land \\
&\qquad  \ \Psi file \in C,\ nontriviallyHolds(r,file)\} 
\end{align*}
\end{small}
\caption{The definition of which rules should be learned by ConfigV when learning over a set of possibly correct, and possibly incorrect files.}
\label{fig:configV}
\end{figure}

We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.
The intuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
and for which we have at least some examples for which that rule is nontrivially true ($\Psi$).
The exact definition and implementation of $\Pi$ and $\Psi$ is a research question still to be solved.
Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
This requires creating some cost function for which the autotuning can optimize.
Additionally, it is possible that $\Pi$ and $\Psi$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
Building a clear formalization and a modular tool to explore these questions is major task.

>>>>

\section{The Learner Module}
\label{sec-learn}

@@

\iffalse
\subsection{Derivation of ConfigC Rules}

@@

\fi

The approach in our earlier work~\cite{santolucitoCAV} is guaranteed to produced only correct rules.
As opposed to a traditional machine learning approach, we have here a formal guarantee of rule coverage.
Furthermore, by design this approach gives a justification (error location) for the classification of a user file as correct or misconfiguration.
This approach is most closely related to version space learning~\cite{mitchell77}, which we discuss further in Sec.~\ref{sec:travis}.

\subsection{Derivation of ConfigV Rules}
\label{subsec-rules}

In \app's learner module, we release the assumption in the above
solution, which means the rule learning mechanism is tolerant 
enough to accept a dataset of possibly incorrect configuration files.
Rather than manually correcting each file, 
we extend the ConfigC formalism to run probabilistic learning
on the intermediate representations.
Our probabilistic approaches for learning missing entry, 
ordering, and fine-grained value correlation rules stem 
from existing work with building 
non-probabilistic versions of these rule-learning algorithms. 
For each of these rules, 
we consider all possible permutations of keys that appear in every 
file which are appropriately typed, and for our learning process, calculate the likelihood that each of 
these permutations constitute a rule. 
Broadly speaking, we accept rule patterns that appear frequently enough.

We now describe a formalism how to compute the set of learned
probabilistic rules, denoted with $\mathcal{PR}$.
With $\mathcal{U}$ we denote a set of configuration files in the 
intermediate representation. If a template can be instantiated with
keywords from file $f$ and the obtained rule $r$ holds, we state that with the predicate 
$\mathit{appears}(r,f)$.
If a template is instantiated and we obtain rule $r$, with  the predicate 
$\mathit{holds}(r,f)$ we state that either $\mathit{appears}(r,f)$ holds, or $r$ could not be instantiated with keywords from $f$. With every 
rule $r$ we define two sets:
\begin{align*}
S_A(r)& =\{ \ f\ | \ \mathit{appears}(r,f)\  \} \\
S_H(r)& =\{ \ f\  | \ \mathit{holds}(r,f) \ \}
\end{align*}
We define then set $\mathcal{PR}$ as
$$\mathcal{PR} = \{\ r \ \mid \ |S_A(r)| > T_1 \land |S_H(r)| > T_2 \ \} $$
where $T_1$ is a threshold value for considering rules which are true in 
majority of cases, and $T_2$ is a threshold value for considering rules 
for which we have at least some examples that that rule is will 
appear in the files.

\ruzica{Read this and weep, Santolucito!}
We use $\Pi$ and $\Psi$ in Fig~\ref{fig:configV} to indicate that the rule holds for some critical portion of the files.
The intuition behind these quantifiers are that we want to consider rules which are true in majority of cases ($\Pi$), 
and for which we have at least some examples for which that rule is nontrivially true ($\Psi$).
The exact definition and implementation of $\Pi$ and $\Psi$ is a research question still to be solved.
Even taking a simple majority voting approach, we must find the cutoff value that will yield the best results in learning.
We plan to try multiple strategies to find these values.
One approach may be to use machine learning for program autotuning, with a tool like OpenTuner~\cite{ansel:pact:2014}.
This requires creating some cost function for which the autotuning can optimize.
Additionally, it is possible that $\Pi$ and $\Psi$ differ depending on the quality of the learning set and/or the particular type of rule being learned.
Building a clear formalization and a modular tool to explore these questions is major task.
